### 2013-04-10 MSteenhagen-CV.tex
Fixed MPhil Stud qualification
Fixed ArtEZ typo
Reformulated TA Heythr description

\ind 2011. MPhil Stud. research student. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\noindent\emph{ARTeZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}

@@

\ind 2009--Present. Tutorial Assistant in Philosophy\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).

>>>>

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\noindent\emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}

@@

\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
